Résultat des simulations

### 2020-10-06 12_Analyse_simulation.Rmd
update script

```{r setup, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8)
# library(kableExtra)
#library(rgl)
#knit_hooks$set(webgl = hook_webgl)
options(scipen=999)
# wkhtmltopdf -B 15 -L 15 -R 15 -T 15 fiche-observatoire.html fiche-observatoire.pdf
# load packages
library(ggplot2)
library(plyr)
#
# set work directory
setwd("/home/jean-matthieu/R/PROTEST")
```

@@

```{r charge.donnees.initiales, echo=FALSE, warning=FALSE, message=FALSE}
# load full file
forestStands <- read.table("./output/forestStandsFULL.txt", header=TRUE, sep = '\t')
forestStands$WKT.GEOM <- as.character(forestStands$WKT.GEOM)
forestStands <- sf::st_sf(forestStands[,-which(names(forestStands)=="WKT.GEOM")], geom=sf::st_as_sfc(forestStands$WKT.GEOM))
sf::st_crs(forestStands) <- 2154
#
# format names
# typologie
levels(forestStands$typologie) <- gsub("Priv", "Privé", levels(forestStands$typologie))
levels(forestStands$typologie) <- gsub("Pub", "Public", levels(forestStands$typologie))
# gestion
levels(forestStands$gestion) <- gsub("AccGere", "Accessible-géré", levels(forestStands$gestion))
levels(forestStands$gestion) <- gsub("AccNonGere", "Accessible-non géré", levels(forestStands$gestion))
levels(forestStands$gestion) <- gsub("NonAcc", "Non accessible", levels(forestStands$gestion))
levels(forestStands$gestion) <- gsub("NonBuch", "Non bûcheronnable", levels(forestStands$gestion))
# itineraire
forestStands$itineraire <- factor(ifelse(substr(forestStands$COMMENT,1,2)=="Co", "Inaction",
                                  ifelse(substr(forestStands$COMMENT,1,2)=="Ir", "Irrégulier",
                                         ifelse(substr(forestStands$COMMENT,1,2)=="Th", "Amélioration","Coupe rase"))))
```

>>>>

```{r setup, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8)
# library(kableExtra)
#library(rgl)
#knit_hooks$set(webgl = hook_webgl)
options(scipen=999)
# wkhtmltopdf -B 15 -L 15 -R 15 -T 15 fiche-observatoire.html fiche-observatoire.pdf
# load packages
library(ggplot2)
library(plyr)
#
# set work directory
setwd("/media/data/R/packages/PROTEST")#"/home/jean-matthieu/R/PROTEST")

@@

```{r charge.donnees.initiales, echo=FALSE, warning=FALSE, message=FALSE}
# load full file
forestStands <- read.table("./output/forestStandsFULL.txt", header=TRUE, sep = '\t', dec=".")
forestStands$WKT.GEOM <- as.character(forestStands$WKT.GEOM)
forestStands <- sf::st_sf(forestStands[,-which(names(forestStands)=="WKT.GEOM")], geom=sf::st_as_sfc(forestStands$WKT.GEOM))
sf::st_crs(forestStands) <- 2154
#
# format names
# typologie
levels(forestStands$typologie) <- gsub("Priv", "Privé", levels(forestStands$typologie))
levels(forestStands$typologie) <- gsub("Pub", "Public", levels(forestStands$typologie))
# gestion
levels(forestStands$gestion) <- gsub("AccGere", "Accessible-géré", levels(forestStands$gestion))
levels(forestStands$gestion) <- gsub("AccNonGere", "Accessible-non géré", levels(forestStands$gestion))
levels(forestStands$gestion) <- gsub("NonAcc", "Non accessible", levels(forestStands$gestion))
levels(forestStands$gestion) <- gsub("NonBuch", "Non bûcheronnable", levels(forestStands$gestion))
# itineraire
forestStands$itineraire <- factor(ifelse(substr(forestStands$COMMENT,1,2)=="Co", "Inaction",
                                  ifelse(substr(forestStands$COMMENT,1,2)=="Ir", "Irrégulier",
                                         ifelse(substr(forestStands$COMMENT,1,2)=="Th", "Amélioration","Coupe rase"))))
```
